A Review on Multi-Label Learning Algorithms

### 2018-01-17 Paper/Presentation/mll_review.tex

\end{itemize}
\end{frame}
%------------------------------------------------
%------------------------------------------------
\subsection{Algorithm Strategies}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Label search space $\mathbb{S_Y}$ grows exponentially as a function of $|Y|=q$
\begin{itemize}
\item[$\triangleright$] e.g. for $q=20, |\mathbb{S_Y}| = 2 ^ {|\mathbb{P(Y)}|} = 2^{20} \ge 10^6$
\end{itemize}
Solution: integrate in the learning process potential label correlations.
This work examines algorithms grouped in three broad categories:

\begin{enumerate}
\item First-order strategies
\begin{itemize}
\item[$\circ$] Ignore label correlations
\item[$\circ$] Often transform M-L problem to multiple, single-label problems
\item[$\circ$] Simple, scalable, suboptimal
\end{itemize}
\item Second-order strategies
\begin{itemize}
\item[$\circ$] Consider \emph{pairwise} label relations
\item[$\circ$] Good trade-off between generalization performance and scalability
\item[$\circ$] Lacking in some real-world applications
\end{itemize}
\item Higher-order strategies
\begin{itemize}
\item[$\circ$] Capture more complicated label interdependencies
\item[$\circ$] Strong modeling capabilities
\item[$\circ$] Computationally demanding, less scalable
\end{itemize}

@@

Two categories and perspectives:
\begin{itemize}
\item[$\bullet$] \emph{Example-based: }Evaluates multi-labeled performance on each example, extrapolate to whole dataset
\begin{itemize}
\item[$\circ$] \emph{Classification perspective:}
\begin{itemize}
\item[$\star$] Subset Accuracy, Hamming Loss
\item[$\star$] Precision, Recall, F-measure, F$^\beta$ -measure
\end{itemize}
\item[$\circ$] \emph{Ranking perspective:} one-error, coverage, ranking loss, average precision
\end{itemize}
\item[$\bullet$] \emph{Label-based: }Evaluates performance on each label separately, extrapolate to whole label set
\begin{itemize}
\item[$\circ$] Classification perspective: Macro/Micro averaging for single-label example-based, classification-based measures
\item[$\circ$] Ranking perspective: Macro/Micro averaging for AUC
\end{itemize}
\end{itemize}
$\ast$ Classifiers should aim to optimize \emph{multiple} metrics
\end{frame}
%------------------------------------------------
\section{Multi-label Learning Algorithms}
%------------------------------------------------
\subsection{Categorization}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Multi-label Learning Algorithms}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : \insertsubsection}

@@

\begin{itemize}
\item[$\circ$] Transform the learning problem into other well-established learning scenarios
\item[$\circ$] ``Fit data to algorithm'' philosophy
\end{itemize}

@@

Include algorithms that:
\begin{itemize}
\item[$\checkmark$] Has broad, noteworthy or unique characteristics
\item[$\checkmark$] Has primitive impact, i.e. leads to a number follow-up related methods
\item[$\checkmark$] Is influential and highly-cited in multi-label learning
\end{itemize}

@@

\begin{itemize}
\item[$\bullet$] Decompose multi-label problem to $q$ independent binary classification problems
\item[$\bullet$] Construct $q$ binary (one-vs-all) training sets (one for each $y_i$)
\item[$\bullet$] Cross-train each binary classifier $h_i(x)$ on its respective dataset

\item[$\bullet$] Predict labels of an unseen $x$ by evaluating each classifier $h_i(x)$
\item[$\bullet$] Assign label $y_i$ according to $h_i(x)$ and the thresholding/ranking scheme 
\end{itemize}

Pros \& cons:
\begin{itemize}
\item[$\bullet$] Simple, one-vs-rest scheme, parallelizable
\item[$\bullet$] Sensitive to class-imbalanced data
\item[$\bullet$] Ignores label correlations (first-order method)
\end{itemize}

@@

\begin{frame}
\frametitle{Classifier chains}
\begin{itemize}
\item[$\bullet$] A permutation function $f_p$ is used to order $Y$
\item[$\bullet$] Transform into a \emph{chain} of binary classification problems
\item[$\bullet$] Enrich representations at step $j$ by concatenating each $x_i$ with the confidence of preceeding $1,\dots,j-1$-th classifiers
\item[$\bullet$] Predict relevant labels for unknown instances by iteratively traversing the classifier chain
\item[$\bullet$] $\lambda_{\tau(j)}^x \in \{-1,+1\}$ represents the predicted binary assignment
of $y_{\tau(j)}$, which is recursively obtained
\end{itemize}

Pros \& cons:
\begin{itemize}
\item[$\bullet$] High-order method: exploitation of label correlations to a degree, but in a random manner
\item[$\bullet$] Highly sensitive to $f_p$. Ensemble schemes attempt to overcome it.
\item[$\bullet$] Iterative operation prevents parallel implementation
\end{itemize}
\end{frame}
%------------------------------------------------

\begin{frame}
\frametitle{Calibrated Label Ranking}
\begin{itemize}
\item[$\bullet$] Transform into a label pairwise comparison ranking problem
\item[$\bullet$] For $q$ labels, generate $q(q-1)/2$ binary classifiers by pairwise comparison and use a binary algorithm $g_{jk}(x)$
\item[$\bullet$] Construct training sets $D_{jk} : \{x_i, Y_i | y_j \in Y_i \oplus y_k \in Y_i\}$. System votes for each example and if $g_{jk}(x) >0$,$x_i$ is associated with $y_j$, otherwise with $y_k$
\item[$\bullet$] For an unknown instance, all classifiers' votes are aggregated and ranked
\item[$\bullet$] A virtual label $y_v$ serves as the artificial splitting point between relevant and irrelevant labels
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] Second-order approach algorithm. One-vs-one scheme.
\item[$\bullet$] Smooths out the class-imbalance problem
\item[$\bullet$] Number of classifiers is quadratic to $|Y|$ (compared to linear for BR)
\begin{itemize}
\item[$\circ$] Pruning methods to reduce the search space
\end{itemize}
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Random k-Labelsets}
\begin{itemize}
\item[$\bullet$] Decompose to an ensemble of multi-class classification problems
\item[$\bullet$] Each component targets a random subset of $\mathbb{P}(Y)$ that appears in $X$, classified with Label Powerset (LP) techniques:
\begin{itemize}
\item[$\circ$] Transform to single-label data by treating each distinct labelset as a new class
\item[$\circ$] Each example is reassigned with the new mapped class and classified through regular single-label classification
\item[$\circ$] M-L classify $x$ with $y_i$ when the votes received for $y_i$ from the ensemble exceed half the max possible it can get
\end{itemize}
todo how does each LP classify, k-labelsets
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] High-order approach algorithm
\item[$\bullet$] Data-sensitive: Cannot generalize to labelsets not in the training set, too few examples for some labelsets
\item[$\bullet$] Large $Y$ implies high training complexity.
\item[$\bullet$] Improve by invoking an ensemble on random k-sized labelsets
\end{itemize}
\end{frame}
%------------------------------------------------
\subsection{Alogrithm Adaptation Methods}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Algorithm Adaptation Methods}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{figure}
\begin{center}
\includegraphics[scale = 0.75]{images/aa.png}
\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Multi-Label k-Nearest Neighbour}
\begin{itemize}
	\item[$\bullet$] Let $H_j \equiv (y_j \in Y_i)$, $C_j = \sum_{x_k \in N(x_i)} [\delta(y_j \in Y_k)]$
\item[$\bullet$] Compares the MAP probabilities: $P(K|C_j), K \in \{H_j, \neg H_j\}$ to decide if to include $y_j$ in the prediction. Compute with the Bayes' theorem.
\item[$\bullet$] Priors $P(K)$ computed by smoothed frequency counting in the training data
\item[$\bullet$] Likelihoods $P(C_j|K)$ are computed as a function of:
\begin{itemize}
\item[$\circ$] $\kappa(r)$, the number of examples labelled $y_j$ with $r$ neighbours labelled $y_j$
\item[$\circ$] $\overset{\sim}{\kappa}(r)$, the number of examples not labelled $y_j$ with $r$ neighbours labelled $y_j$
\end{itemize}
\end{itemize}

Pros \& cons:
\begin{itemize}
\item[$\bullet$] First-order approach, Bayesian reasoning
\item[$\bullet$] Decision boundary can be modified on-line via new instances
\item[$\bullet$] Class imbalance can be overcome by calculating priors
\item[$\bullet$] Extensions proposed for label correlation exploitations
\end{itemize}

\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Multi-label Decision Tree}
\begin{itemize}
\item[$\bullet$] Multi-label entropy is used to build a decision tree recursively
\item[$\bullet$] Split $x$ at feature $l$ s.t. the information gain criterion is maximized
\item[$\bullet$] Dataset $T$ is split on the $l$-th feature valued $\theta$ to branches ($T^-$ \& $T^+$), where $ x_{il} \leq \theta, x_i \in T^-$ and $ x_{il} > \theta, x_i \in T^+$
\item[$\bullet$] Recurse on subtrees until a stopping criterion is met (e.g. child size)
\item[$\bullet$] Single-label entropy is computed by considering labelsets as new classes
\item[$\bullet$] Assumes independence among labels to ensure low computational cost
\item[$\bullet$] Unseen instances are assigned the label of the majority of members of the leaf they arrive
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] First-order algorithm, highly efficient
\item[$\bullet$] Assumes label independence
\item[$\bullet$] Pruning and ensemble strategies proposed
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Ranking Support Vector Machine}
\begin{itemize}
	\item[$\bullet$] $q$ linear classifiers $h_i(x)$, optimized with the empirical ranking loss
\item[$\bullet$] Relevant-nonrelevant label pairs of $x_i$: $(y_j,y_k) \in Y_i
  \times \bar Y_i$: decision hyperplane\footnote{w.r.t. singed classifier distance} is: $h_j, h_k$: $\left<w_j-w_k, x_i \right> + b_j - b_k=0$
\item[$\bullet$] Separation margin is the minimum distance of $x_i$ from every  $Y_i \times \bar Y_i$
\item[$\bullet$] SVM $\rightarrow$ minimize loss \emph{and} maximize margin.
  Approximate $max(\cdot)$ and introduce slack variables.

\item[$\bullet$] Ranks labels w.r.t. singled distance
\item[$\bullet$] Non-linearity achievable through feature mapping and the kernel trick
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] Second-order approach, maximum margin strategy
\item[$\bullet$] Convex quadratic programming problem, solved by any QP solver
\item[$\bullet$] Extensible by kernel learning: kernel selection can be overcome by Multiple Kernel Learning techniques
\item[$\bullet$] Adaptable learning by selecting an appropriate loss function
\end{itemize}

\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Collective Multi-Label Classifier}
\begin{itemize}
\item[$\bullet$] Encodes labels as binary random vectors $\bm{y}=\{-1,1\}\}^q$
\item[$\bullet$] For data $x,\bm{y}$ learn joint probability distribution $p(x,\bm{y})$
\item[$\bullet$] Learn pdf $p(x,\bm{y})$ via the principle of maximun entropy
  \begin{itemize}
    \item Maximize $H_p(x,y)$ subject to $K$ constraints $\mathbb{E}[f_k(x,\bm{y})] = F_k$
    \item $f_k$ models label correlations with $F_k$ learned from the training data
  \end{itemize}
\item[$\bullet$] Optimize via Lagrange multipliers, arrive at $p(\bm{y} | x)$
\item[$\bullet$] Unseen instances labelled with $Y = \underset{y}{\text{argmax }} p(y | x)$
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] Second-order approach. All label pairs considered, not just relevant-irrelevant ones.
\item[$\bullet$] Convex constraint optimization problem $\rightarrow$ solvable by any
  CP solver
\item[$\bullet$] Intractable $\text{argmax}$ operation for a large label space without pruning.
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : Summary}
\begin{figure}
\begin{center}
\includegraphics[scale = 0.45]{images/summary.png}
\caption{Summary of Representative Multi-Label Learning Algorithms}
\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\section{Related Learning Settings}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection}
\begin{itemize}
\item[$\bullet$] Multi-instance learning
  % https://en.wikipedia.org/wiki/Multiple-instance_learning
\begin{itemize}
\item[$\circ$] Instead of labeled instances, get binary-labeled \emph{bags of instances}
\item[$\circ$] Assign positive label to bag if at least one member is positive
\item[$\circ$] Models complex semantics of $x_i$ in input space, rather than its output
\end{itemize}
\item[$\bullet$] Ordinal classification
  % https://en.wikipedia.org/wiki/Ordinal_regression
\begin{itemize}
\item[$\circ$] Assume labels are related through a natural ordering
\item[$\circ$] Instead of explicit class relevance, assume an ordering of
  relevance between labels via a membership vector
\item[$\circ$] Transform ML problem to a set of ordinal set of problems
\end{itemize}
\item[$\bullet$] Multi-task learning
\begin{itemize}
\item[$\circ$] Multiple tasks trained in parallel, sharing information
\item[$\circ$] Knowledge from related tasks used as an inductive bias to improve generalization
\item[$\circ$] Shared or different feature space, small task workload
\end{itemize}
\item[$\bullet$] Data streams classification
\begin{itemize}
\item[$\circ$] Real-world objects are generated online and processed in  real-time
\item[$\circ$] Concept drift problem
\end{itemize}
\end{itemize}
\end{frame}

%------------------------------------------------
\section{Conclusion}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Conclusion}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection}
Summary:
\begin{itemize}
\item[$\bullet$] Multi-label learning problem definition
\item[$\bullet$] Multi-label learning representative algorithms
\item[$\bullet$] Related learning settings
\end{itemize}

Future goals:
\begin{itemize}
\item[$\bullet$] Holy grail: Formal characterization on the underlying concept / mechanism on the appropriate usage of label correlations, especially on large output spaces
\item[$\bullet$] Thorough experimental comparative study to discover pros and cons of different multi-label learning algorithms
\end{itemize}
\end{frame}

%------------------------------------------------
\subsection{Online resources}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{figure}
	\begin{center}
		\includegraphics[scale = 0.47]{images/online.png}
		\caption{Online Resources for Multi-Label Learning}
	\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\subsection{Related Work}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{itemize}
\item[$\bullet$] Madjarov, Gjorgji, et al. "An extensive experimental comparison of methods for multi-label learning." Pattern Recognition 45.9 (2012): 3084-3104
\item[$\bullet$] Tsoumakas, Grigorios, and Ioannis Katakis. "Multi-label classification: An overview." International Journal of Data Warehousing and Mining 3.3 (2006)
\item[$\bullet$] Zhang, Min-Ling, and Kun Zhang. "Multi-label learning by exploiting label dependency." Proceedings of the 16th ACM SIGKDD international conference on Knowledge discovery and data mining. ACM, 2010
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Useful additional bibliography
\begin{itemize}
\item[$\bullet$] Elisseeff, André, and Jason Weston. "A kernel method for multi-labelled classification." Advances in neural information processing systems. 2002.
\item[$\bullet$]  Ghamrawi, Nadia, and Andrew McCallum. "Collective multi-label classification." Proceedings of the 14th ACM international conference on Information and knowledge management. ACM, 2005.
\end{itemize}
\end{frame}
%------------------------------------------------
\section{The end}
\begin{frame}
\Huge{\centerline{Thank you}}
\Huge{\centerline{Questions?}}
\end{frame}
%------------------------------------------------
\end{document}

>>>>

\end{itemize}
\end{frame}
%------------------------------------------------
%------------------------------------------------
\subsection{Algorithm Strategies}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Label search space $\mathbb{S_Y}$ grows exponentially as a function of $|Y|=q$
\begin{itemize}
\item[$\triangleright$] e.g. for $q=20, |\mathbb{S_Y}| = 2 ^ {|\mathbb{P(Y)}|} = 2^{20} \ge 10^6$
\end{itemize}
Solution: integrate in the learning process potential label correlations.

In this work the authors group M-L algorithms in three categories:

\begin{enumerate}
\item First-order strategies
\begin{itemize}
\item[$\circ$] Ignore label correlations
\item[$\circ$] Often transform M-L problem to multiple, single-label problems
  and combine the per-label results
\item[$\circ$] Simple, scalable, suboptimal
\end{itemize}
\item Second-order strategies
\begin{itemize}
\item[$\circ$] Consider \emph{pairwise} label relations
\item[$\circ$] Good trade-off between generalization performance and scalability
\item[$\circ$] Lacking in some real-world applications
\end{itemize}
\item Higher-order strategies
\begin{itemize}
\item[$\circ$] Capture more complicated label interdependencies
\item[$\circ$] Strong modeling capabilities that can capture complex relationships
\item[$\circ$] Computationally demanding, less scalable
\end{itemize}

@@

Grouped into two categories and perspectives:
\begin{itemize}
\item[$\bullet$] \emph{Example-based: }Evaluates multi-labeled performance on each example, extrapolate to whole dataset
\begin{itemize}
\item[$\circ$] \emph{Classification perspective:}
\begin{itemize}
\item[$\star$] Subset Accuracy, Hamming Loss
\item[$\star$] Precision, Recall,  F$^\beta$ -measure
\end{itemize}
\item[$\circ$] \emph{Ranking perspective:} one-error, coverage, ranking loss, average precision
\end{itemize}
\item[$\bullet$] \emph{Label-based: }Evaluates performance on each label separately, extrapolate to whole label set
\begin{itemize}
\item[$\circ$] Classification perspective: Macro/Micro averaging techniques for single-label example-based, classification-perspective measures
\item[$\circ$] Ranking perspective: Macro/Micro averaging for AUC
\end{itemize}
\end{itemize}
$\ast$ Ideally, classifiers should be trained to optimize \emph{multiple} metrics
\end{frame}
%------------------------------------------------
\section{Multi-label Learning Algorithms}
%------------------------------------------------
\subsection{Categorization}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Multi-label Learning Algorithms}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : \insertsubsection}

@@

\begin{itemize}
\item[$\circ$] Transform the learning problem into other, managable (often
  single-label) learning
  problems 
\item[$\circ$] ``Fit data to algorithm'' philosophy
\end{itemize}

@@

Authors include algorithms that:
\begin{itemize}
\item[$\checkmark$] Has broad, noteworthy or unique characteristics
\item[$\checkmark$] Has important impact, leading to a number follow-up related methods
\item[$\checkmark$] Is influential and highly-cited in multi-label learning
\end{itemize}

@@

\begin{itemize}
\item[$\bullet$] Decompose multi-label problem to $|Y|=q$ independent binary classification problems
\item[$\bullet$] Construct $q$ binary (one-vs-all) training sets (one for each $y_i$)
\item[$\bullet$] Independently train each classifier $h_i(x)$ on its respective dataset

\item[$\bullet$] Predict labels of an unseen $x$ by evaluating each classifier $h_i(x)$
\item[$\bullet$] Assign label $y_i$ according to $r = h_i(x)$ and the
  thresholding setting 
\end{itemize}

Pros \& cons:
\begin{itemize}
\item[$\bullet$] Simple, one-vs-rest scheme $\rightarrow$ easily parallelizable
\item[$\bullet$] Sensitive to class-imbalanced data\footnote{Very different
    number of pos. and neg. examples for a class}
\item[$\bullet$] Ignores label correlations (first-order method)
\end{itemize}

@@

\begin{frame}
\frametitle{Classifier chains}
\begin{itemize}
\item[$\bullet$] Reorder the label $Y$ set using a permutation function $f_p$ 
\item[$\bullet$] Transform into a \emph{chain} of binary classification problems
\item[$\bullet$] Enrich representations at step $j$ by concatenating each $x_i$ with the confidence of preceeding $1,\dots,j-1$-th classifiers
\item[$\bullet$] Predict relevant labels for unknown instances by iteratively traversing the classifier chain
\end{itemize}

Pros \& cons:
\begin{itemize}
\item[$\bullet$] High-order method: exploitation of label correlations to a degree, but in a random manner
\item[$\bullet$] Highly sensitive to $f_p$. Running multiple chain executions in an ensemble
  attempt to overcome this dependency.
\item[$\bullet$] Iterative operation prevents parallel implementation
\end{itemize}
\end{frame}
%------------------------------------------------

\begin{frame}
\frametitle{Calibrated Label Ranking}
\begin{itemize}
\item[$\bullet$] Transform into a label pairwise comparison ranking problem
\item[$\bullet$] For $q$ labels, generate $q(q-1)/2$ binary classifiers by pairwise comparison and use a binary algorithm $h_{jk}(x)$
\item[$\bullet$] Construct training sets $D_{jk} : \{x_i, Y_i | y_j \in Y_i \oplus y_k \in Y_i\}$. System votes for each example and if $h_{jk}(x) >0$,$x_i$ is associated with $y_j$, otherwise with $y_k$
\item[$\bullet$] For an unknown instance, all classifiers' votes are aggregated
  and resulting labels are ranked according to the total confidence $r$
\item[$\bullet$] A virtual label $y_v$ is learned as a threshold, serving as the artificial splitting point between relevant and irrelevant labels
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] Second-order approach algorithm. One-vs-one scheme.
\item[$\bullet$] Pairwise comparison smooths out the class-imbalance problem
\item[$\bullet$] Number of classifiers is quadratic to $|Y|$ (compared to linear for BR)
\begin{itemize}
\item[$\circ$] Pruning methods to reduce the search space
\end{itemize}
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Random k-Labelsets}
\begin{itemize}
\item[$\bullet$] Decompose to an ensemble of multi-class classification problems
\item[$\bullet$] Each component targets a random subset of $\mathbb{P}(Y)$ (that
  also appears in $X$), classified with Label Powerset (LP) techniques:
\begin{itemize}
\item[$\circ$] Transform to single-label data by treating each distinct labelset
  as a new class $\rightarrow$ multi to single label problem
\item[$\circ$] Each example is reassigned with the new mapped class and classified through regular single-label classification
\item[$\circ$] M-L classify $x$ with $y_i$ when the votes received for $y_i$ from the ensemble exceed half the max possible it can get
\end{itemize}
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] High-order approach algorithm
\item[$\bullet$] Data-sensitive: Cannot generalize to labelsets not in the training set, too few examples for some labelsets
\item[$\bullet$] Large $Y$ implies high training complexity.
\item[$\bullet$] Improve by invoking an ensemble on random k-sized labelsets
\end{itemize}
\end{frame}
%------------------------------------------------
\subsection{Alogrithm Adaptation Methods}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Algorithm Adaptation Methods}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{figure}
\begin{center}
\includegraphics[scale = 0.75]{images/aa.png}
\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Multi-Label k-Nearest Neighbour}
\begin{itemize}
	\item[$\bullet$] Let $H_j \equiv (y_j \in Y_i)$, $C_j = \sum_{x_k \in N(x_i)} [\delta(y_j \in Y_k)]$
\item[$\bullet$] Compares the MAP probabilities: $P(K|C_j), K \in \{H_j, \neg H_j\}$ to decide if to include $y_j$ in the prediction. Compute with the Bayes' theorem.
\item[$\bullet$] Single-label priors $P(K)$ computed by smoothed frequency counting in the training data
\item[$\bullet$] Likelihoods $P(C_j|K)$ are computed as a function of:
\begin{itemize}
\item[$\circ$] $\kappa(r)$, the number of examples labelled $y_j$ with $r$ neighbours labelled $y_j$
\item[$\circ$] $\overset{\sim}{\kappa}(r)$, the number of examples not labelled $y_j$ with $r$ neighbours labelled $y_j$
\end{itemize}
\end{itemize}

Pros \& cons:
\begin{itemize}
\item[$\bullet$] First-order approach, Bayesian reasoning
\item[$\bullet$] Decision boundary can be modified on-line via new instances
\item[$\bullet$] M-L class imbalance can be overcome by calculating the priors
\item[$\bullet$] Extensions proposed for label correlation exploitations
\end{itemize}

\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Multi-label Decision Tree}
\begin{itemize}
\item[$\bullet$] Multi-label entropy is used to build a decision tree recursively
\item[$\bullet$] Split $x$ at the $l$-th feature\footnote{$x$ has to contain distinct features} s.t. the information gain criterion is maximized
\item[$\bullet$] Dataset $T$ is split on the $l$-th feature valued $\theta$ to branches ($T^-$ \& $T^+$), where $ x_{il} \leq \theta, x_i \in T^-$ and $ x_{il} > \theta, x_i \in T^+$
\item[$\bullet$] Recurse on subtrees until a stopping criterion is met (e.g. child size)
\item[$\bullet$] Single-label entropy is computed by considering labelsets as new classes
\item[$\bullet$] Assumes independence among labels to ensure low computational cost
\item[$\bullet$] Unseen instances are assigned the label of the majority of members of the leaf they arrive
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] First-order algorithm, highly efficient
\item[$\bullet$] Assumes label independence
\item[$\bullet$] Pruning and ensemble strategies proposed
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Ranking Support Vector Machine}
\begin{itemize}
	\item[$\bullet$] $q$ linear classifiers $h_i(x)$, optimized with the empirical ranking loss
\item[$\bullet$] Consider signed distance of $x_i$ from the boundary of every
  relevant-nonrelevant label pair $(y_j,y_k) \in Y_i \times \bar Y_i$. The
  pair's decision hyperplane is: $h_j, h_k$: $\left<w_j-w_k, x_i \right> + b_j - b_k=0$
\item[$\bullet$] The M-L margin is the minimum distance of $x_i$ from every  $Y_i \times \bar Y_i$
\item[$\bullet$] SVM $\rightarrow$ minimize loss \emph{and} maximize margin.
  Approximate $max(\cdot)$ and introduce slack variables.

\item[$\bullet$] Ranks labels according to the singed distance
\item[$\bullet$] Non-linearity achievable through feature mapping and the kernel trick
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] Second-order approach, maximum margin strategy
\item[$\bullet$] Convex quadratic programming problem, solved by any QP solver
\item[$\bullet$] Extensible by kernel learning: kernel selection can be overcome by Multiple Kernel Learning techniques
\item[$\bullet$] Adaptable learning by selecting an appropriate loss function
\end{itemize}

\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Collective Multi-Label Classifier}
\begin{itemize}
\item[$\bullet$] Encodes labels as binary random vectors $\bm{y}=\{-1,1\}\}^q$
\item[$\bullet$] For data $x,\bm{y}$ learn joint probability distribution $p(x,\bm{y})$
\item[$\bullet$] Learn pdf $p(x,\bm{y})$ via the principle of maximun entropy
  \begin{itemize}
    \item Maximize $H_p(x,y)$ subject to $K$ constraints $\mathbb{E}[f_k(x,\bm{y})] = F_k$
    \item $f_k$ models label correlations with $F_k$ learned from the training data
  \end{itemize}
\item[$\bullet$] Optimize via Lagrange multipliers, arrive at $p(\bm{y} | x)$
\item[$\bullet$] Unseen instances labelled with $Y = \underset{y}{\text{argmax }} p(y | x)$
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] Second-order approach. All label pairs considered, not just relevant-irrelevant ones.
\item[$\bullet$] Convex constraint optimization problem $\rightarrow$ solvable by any
  CP solver
\item[$\bullet$] Intractable $\text{argmax}$ operation for a large label space without pruning.
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : Summary}
\begin{figure}
\begin{center}
\includegraphics[scale = 0.45]{images/summary.png}
\caption{Summary of Representative Multi-Label Learning Algorithms}
\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\section{Related Learning Methods}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection}
\begin{itemize}
\item[$\bullet$] Multi-instance learning
  % https://en.wikipedia.org/wiki/Multiple-instance_learning
\begin{itemize}
\item[$\circ$] Instead of labeled instances, get binary-labeled \emph{bags of instances}
\item[$\circ$] Assign positive label to bag if at least one member is positive
\item[$\circ$] Models complex semantics of $x_i$ in input space, rather than its output
\end{itemize}
\item[$\bullet$] Ordinal classification
  % https://en.wikipedia.org/wiki/Ordinal_regression
\begin{itemize}
\item[$\circ$] Assume labels are related through a natural ordering
\item[$\circ$] Instead of explicit class relevance, assume an ordering of
  relevance between labels via a membership vector
\item[$\circ$] Transform ML problem to a set of ordinal set of problems
\end{itemize}
\item[$\bullet$] Multi-task learning
\begin{itemize}
\item[$\circ$] Multiple tasks trained in parallel, sharing information
\item[$\circ$] Knowledge from related tasks used as an inductive bias to improve generalization
\item[$\circ$] Shared or different feature space, small task workload
\end{itemize}
\item[$\bullet$] Data streams classification
\begin{itemize}
\item[$\circ$] Real-world objects are generated online and processed in  real-time
\item[$\circ$] Concept drift problem
\end{itemize}
\end{itemize}
\end{frame}

%------------------------------------------------
\section{Conclusion}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Conclusion}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection}
Summary:
\begin{itemize}
\item[$\bullet$] Multi-label learning problem definition
\item[$\bullet$] Multi-label learning representative algorithms
\item[$\bullet$] Related learning methods
\end{itemize}

Future goals:
\begin{itemize}
\item[$\star$] Formal characterization on the underlying concept / mechanism on the appropriate usage of label correlations, especially on large output spaces
\item[$\bullet$] Thorough experimental comparative study to discover pros and cons of different multi-label learning algorithms
\end{itemize}
\end{frame}

%------------------------------------------------
\subsection{Online resources}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{figure}
	\begin{center}
		\includegraphics[scale = 0.47]{images/online.png}
		\caption{Online Resources for Multi-Label Learning}
	\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\subsection{Related Work}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{itemize}
\item[$\bullet$] Madjarov, Gjorgji, et al. "An extensive experimental comparison of methods for multi-label learning." Pattern Recognition 45.9 (2012): 3084-3104
\item[$\bullet$] Tsoumakas, Grigorios, and Ioannis Katakis. "Multi-label classification: An overview." International Journal of Data Warehousing and Mining 3.3 (2006)
\item[$\bullet$] Zhang, Min-Ling, and Kun Zhang. "Multi-label learning by exploiting label dependency." Proceedings of the 16th ACM SIGKDD international conference on Knowledge discovery and data mining. ACM, 2010
\end{itemize}
\end{frame}
%------------------------------------------------

\subsection{Additional Bibliography}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{itemize}
\item[$\bullet$] Elisseeff, André, and Jason Weston. "A kernel method for multi-labelled classification." Advances in neural information processing systems. 2002.
\item[$\bullet$]  Ghamrawi, Nadia, and Andrew McCallum. "Collective multi-label classification." Proceedings of the 14th ACM international conference on Information and knowledge management. ACM, 2005.
\end{itemize}
\end{frame}
%------------------------------------------------
\section{The end}
\begin{frame}
\Huge{\centerline{Thank you}}
\Huge{\centerline{Questions?}}
\end{frame}
%------------------------------------------------
\end{document}
